---
title: "Binary Choice Analysis"
author: "Robert Hickman"
output:
  pdf_document:
    fig_width: 10
    fig_height: 8
  html_document: default
---
```{r, warning = FALSE, message = FALSE, include = FALSE}
require(ggplot2)
require(ggthemes)
require(dplyr)
require(magrittr)
require(data.table)
require(tidyr)
```

```{r, warning = FALSE, message = FALSE, include = FALSE}
#load in specific data
date <- "27-Dec-2017"
monkey <- "Ulysses"

search_string <- paste0(date, ".*", monkey, "COMPACT")

#find all data files
directory <- "C:/Users/WS-Guest/Desktop/task data/"
data_files <- dir(directory)

#load in the relevant data
specific_files <- data_files[grep(search_string, data_files)]
specific_files <- specific_files[1]

task_data <- rbindlist(lapply(paste0(directory, specific_files), read.csv, na.strings = "NaN"), idcol = "block") %>%
  #munge the data
  .[, block := paste("block", block)] %>%
  .[, trial:= 1:.N, block] %>%
  .[bundle_position == 1, bundle_distance := (monkey_final_bid + 1)/2] %>%
  .[bundle_position == 0, bundle_distance := (1-monkey_final_bid)/2] %>%
  .[bundle_distance < 0.5, fractal_bid := 1] %>%
  .[bundle_distance > 0.5, fractal_bid := 0] %>%
  .[, offer_ml := paste0(((offer_value*2)-1) * 0.15, "ml")] %>%
  .[, bundle_liquid := 1.2 - (bundle_water_perc * 1.2)]

```

Data shown for:
```{r, warning = FALSE, message = FALSE}
date
monkey

```


```{r, warning = FALSE, message = FALSE, include = FALSE}
#plot the left vs right choices of the monkey
p1 <- ggplot(data = task_data, aes(x = monkey_final_bid, y = bundle_position)) +
  geom_point(alpha = 0.4, aes(colour = trial, size = offer_value, shape = as.factor(fractal_bid))) +
  scale_colour_continuous(low = "blue", high = "red", name = "trial number") +
  scale_size_continuous(range = c(4,6), name = "juice offered") +
  scale_shape_manual(values = c(15,16), name = "juice chosen") +
  xlab("bid position") +
  ylab("fractal position") +
  annotate("text", label = "left bid", x = -0.5, y = 0.45, size = 7, colour = "darkgrey") +
  annotate("text", label = "right bid", x = 0.5, y = 0.45, size = 7, colour = "darkgrey") +
  ggtitle("Monkey Bid Positions on Binary Choice Task",
          subtitle = paste(date, ";", monkey, ";", length(unique(task_data$block)), "blocks")) +
  #theme_fivethirtyeight() +
  theme_minimal() +
  theme(strip.text.x = element_text(size = 14)) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14)) +
  facet_wrap("block")

```

```{r, message = FALSE, warning = FALSE}
#plot p1
p1
```

Graph of choices for each block. Circles indicate bid selecting the bundle, squares are bid selecting the budget. A fractal bid position of 1 means that the bundle is on the left hand side of the screen. Bids range from -1 (all the way to the left) to 1 (all the way to the right) \newpage

```{r, warning = FALSE, message = FALSE, include = FALSE}
#plot the distance from the bundle (0-1 of screen width) of the final bid
p2 <- ggplot(data = task_data, aes(x = bundle_distance, colour = as.factor(offer_ml))) +
  geom_freqpoly(size = 3, alpha = 0.75) +
  scale_colour_brewer(palette = "Set1", name = "fractal value") +
  xlab("bid distance from bundle edge") +
  ylab("count") +
  annotate("text", label = "bundle bid", x = 0.05, y = 4, size = 7, colour = "darkgrey") +
  annotate("text", label = "budget bid", x = 0.75, y = 4, size = 7, colour = "darkgrey") +
  ggtitle("Monkey Bid Distance From Bundle on Binary Choice Task",
          subtitle = paste(date, ";", monkey, ";", length(unique(task_data$block)), "blocks")) +
  #theme_fivethirtyeight() +
  theme_minimal() +
  theme(strip.text.x = element_text(size = 14)) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))

```

```{r, warning = FALSE, message = FALSE}
#plot p2
p2
```

Graph showing all choices and how far away they are from the edge of the screen on the bundle side. 0 indicates full movement to the bundle side of the screen and 1 represent full movement away. Count is over all blocks for all values of the fractal (in ml of juice). \newpage

```{r, warning = FALSE, message = FALSE, include = FALSE}
#gather the data with respect the the distance from the bundle that the monkey bid
p3 <- task_data %>%
  .[, c("bundle_position", "bundle_water_perc", "offer_value", "trial", "bundle_distance", "block")] %>%
  gather(-c(bundle_distance, block), key = "var", value = "value") %>%
  #plot the monkeys bundle distance against all other variables
  ggplot(aes(x = value, y = bundle_distance)) +
  geom_point(alpha = 0.6, size = 2, aes(colour = block)) +
  stat_smooth() +
  scale_color_brewer(palette = "Set1", name = "Block") +
  coord_flip() +
  ggtitle("Monkey Bid Distance From Bundle on Binary Choice Task",
          subtitle = paste(date, ";", monkey, ";", length(unique(task_data$block)), "blocks")) +
  #theme_fivethirtyeight() +
  theme_minimal() +
  theme(strip.text.x = element_text(size = 14)) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14)) +
  facet_wrap(~ var, scales = "free")

```

```{r, warning = FALSE, message = FALSE}
#plot p3
p3
```

Graphs of various factors against the distance from the bundle side of the screen the monkey bids.

A bundle position of 1 indicates that the bundle is on the left hand side of the screen. A bundle water percentage of 1 indicates that the bundle contains no water [CHECK THIS- PRETTY SURE ITS CORRECT], whereas zero means it contains the full 1.2ml. Offer values of 1, 2, and 3 represent 0.15ml, 0.45ml, and 0.75mls of apple and mango juice (150ml in 950ml of water).

Fit lines use LOESS method. \newpage

```{r, warning = FALSE, message = FALSE}
#generate a model of likelihood to bid for the fractal dependent on it's position,
#value and associated water
model <- glm(data = task_data,
             fractal_bid ~ bundle_position + bundle_water_perc + offer_value + trial,
             family = "binomial")

#summarise the parameters
summary(model)

```
\newpage


```{r, warning = FALSE, message = FALSE, include = FALSE}
p4 <- task_data[!is.na(fractal_bid), .(.N), by = .(offer_value, bundle_liquid)] %>%
  ggplot(aes(x = ((offer_value*2 -1) * 0.15), y = bundle_liquid * 1.2)) +
  geom_tile(aes(fill = N)) +
  scale_fill_continuous(low = "lightblue", high = "darkred", name = "number of trials") +
  xlab("bundle juice offered (ml)") +
  ylab("bundle water offered (ml)") +
  ggtitle("Monkey Bundle Trials on Binary Choice Task",
          subtitle = paste(date, ";", monkey, ";", length(unique(task_data$block)), "blocks")) +
  #theme_fivethirtyeight() +
  theme_minimal() +
  theme(strip.text.x = element_text(size = 14)) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14)) 

```

```{r, warning = FALSE, message = FALSE}
#plot p4
p4
```

Graph showing the number of trials the monkey carried out for each bundle combination. Does not include failed trials. \newpage

```{r, warning = FALSE, message = FALSE, include = FALSE}
bundle_bidding <- task_data[!is.na(fractal_bid)] %>%
  .[, mean(fractal_bid), by = .(offer_value, bundle_liquid)]

binomial_smooth <- function(...) {
  geom_smooth(method = "glm", method.args = list(family = "binomial"), ...)
}

p5 <- ggplot(bundle_bidding, aes(y = V1, x = bundle_liquid * 1.2, colour = as.factor((offer_value*2 -1) * 0.15))) +
  geom_point(size = 3, alpha = 0.5) +
  binomial_smooth(se = FALSE) +
  scale_colour_brewer(palette = "Set1", name = "juice offered (ml)") +
  xlab("water offered (ml)") +
  ylab("proportion of bundle choices") +
  ggtitle("Monkey Proportion of Bundle Bids on Binary Choice Task",
          subtitle = paste(date, ";", monkey, ";", length(unique(task_data$block)), "blocks")) +
  #theme_fivethirtyeight() +
  theme_minimal() +
  theme(strip.text.x = element_text(size = 14)) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14)) 
```

```{r, warning = FALSE, message = FALSE}
#plot p5
p5
```

Graph showing the proportion of bids for the bundle that a monkey makes, separated by the values of the juice offered in the bundles. Fits using a binomial glm model.

```{r, warning = FALSE, message = FALSE, include = FALSE}
#create a plot like the above but that also plots a 95% confidence interval
#uses the default bionmial smooth CIs- check how these work
p6 <- ggplot(task_data, aes(y = fractal_bid, x = bundle_liquid * 1.2,
                            colour = as.factor((offer_value*2 -1) * 0.15), group = offer_value)) +
  geom_point(size = 3, alpha = 0.2) +
  binomial_smooth(se = TRUE) +
  scale_colour_brewer(palette = "Set1", name = "juice offered (ml)") +
  xlab("water offered (ml)") +
  ylab("proportion of bundle choices") +
  ggtitle("Monkey Proportion of Bundle Bids on Binary Choice Task (CI = 0.95?)",
          subtitle = paste(date, ";", monkey, ";", length(unique(task_data$block)), "blocks")) +
  #theme_fivethirtyeight() +
  theme_minimal() +
  theme(strip.text.x = element_text(size = 14)) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14)) 

```

```{r, warning = FALSE, message = FALSE}
p6
```

Same graph as above but with 95% confidence intervals. Uses the default method of calculating this for the tidyverse libraries in R which I'm not convinced are the best way. Looking into calculating and plotting it myself.


